---
---
---

# 2023 Statistics HW1

311554032 æ•¸æ“šæ‰€ å»–å­æ¿¬

## 1.

### 1a. **(10 points) Please plot the data with X indicating "Percent returning" and Y indicating "New adults". Comment on the main features of the plot. Any possible outliers? (å¯ç”¨è»Ÿé«”ç•«)**

```{r}
# Percent returning


x = c(74, 66, 81, 52, 73, 62, 52, 45, 62, 46, 60, 46, 38)



# New adults


y = c(5, 6, 8, 11, 12, 15, 16, 17, 18, 18, 19, 20, 20)

plot(x, y, col = 'red', main = 'Bird Colonies', xlab = 'Percent returning', ylab = 'New adults')
```

### 1b. **(10 points) Apply the formula to compute \... å¯ä»¥ç”¨é›»è…¦å”åŠ©æ“ä½œå…¬å¼**

mean of X:

```{r}
result.mean <- mean(x)
print(result.mean)
```

mean of Y:

```{r}
result.mean <- mean(y)
print(result.mean)
```

Var of X:

```{r}
print(sum((x-mean(x))^2)/(length(x)-1))
```

Var of Y:

```{r}
print(sum((y-mean(y))^2)/(length(y)-1))
```

Pearson's correlation:

```{r}
print(cor(x, y, method = 'pearson'))
```

### 1c. **(10 points) Use R (è»Ÿé«”) to compute Pearson's correlation, Kendall's tau and Spearman's rho. (ç›¸é—œä¿‚æ•¸æŒ‡ä»¤åœ¨è¬›ç¾©)**

Pearson's Correlation

```{r}
(stddev = sum((x - mean(x)) * (y - mean(y))) / sqrt(sum((x - mean(x))^2) * sum((y - mean(y))^2)))
```

Spearman's rho

```{r}
r_x = rank(x)
r_y = rank(y)
print(r_x)
print(r_y)
# z = sum((r_x-mean(r_x))(r_y-mean(r_y))) / (length(x)-1)
sd(r_x)
sd(r_y)
print(1-(6*sum((r_x-r_y)^2)/(13*168)))
```

Kendall's tau

```{r}
library(DescTools)
tab <- table(x, y)
ConDisPairs(tab)[c("C","D")]
```

```{r}
(14-59)/(13*6)
```

### **1d. (15 points) Please fit the regression model:**

```{r}
df <- data.frame(x, y)
lm.fit <-lm(y ~ x , data=df)
summary(lm.fit)
coef(lm.fit)

#get model summary
model_summ <-summary(lm.fit)
#calculate MSE
mean(model_summ$residuals^2)
```

### 1e. (5 points) What is the value of ... Is it true that R^2^ = r^2^

ans: No, according to the result above, R^2^: 0.5602, r^2^: 0.5202

### 1f. Please plot e ï€½ Y ï€­ Y (Y axis) versus Y (X axis). Comment on the residual plot. What does this plot indicate?

```{r}
res <- resid(lm.fit)
#produce residual vs. fitted plot
plot(fitted(lm.fit), res)

#add a horizontal line at 0 
abline(0,0)
```

No pattern in residual plot. Model is sounded.

## 2 (45 points) å…¨éƒ¨ç”¨è»Ÿé«”çš„æŒ‡ä»¤

### 2a. (10 points) Please plot the data with X indicating "Soda" and Y indicating "Milk". Comment on the main features of the plot. Any possible outliers? é€™è£¡æˆ‘ å»ºè­°æŠŠ Milk ç•¶æˆ Y, æ˜¯å› ç‚ºç‰›å¥¶æ”å–æ˜¯ç‡Ÿé¤Šå­¸å®¶æˆ–å®¶é•·æ¯”è¼ƒåœ¨æ„çš„.

```{r}
#Soda
x = c(35.1, 35.7, 46.2, 47.4, 47.9, 49.7, 49.3)
#Milk
y = c(27.6, 26.7, 25.7, 23.9, 23.0, 22.9, 23.3)
plot(x, y, col = 'red', main = 'Milk or Soda?', xlab = 'Soda', ylab = 'Milk')
```

Two points on the upper left of figure might be the outliers.

### 2b. (10 points) Use R (è»Ÿé«”) to compute Pearson's correlation, Kendall's tau and Spearman's rho.

```{r}
cor.test(x,y,alternative = "two.sided",method = "pearson")
cor.test(x,y,alternative = "two.sided",method = "spearman")
cor.test(x,y,alternative = "two.sided",method = "kendall")
```

### 2c. (10 points) Use R to fit the regression model: Show your output and explain the meaning of ï¢ .

```{r}
df = data.frame(x, y)
lm.fit <-lm(y ~ x , data=df)
summary(lm.fit)
coef(lm.fit)

#get model summary
model_summ <-summary(lm.fit)
#calculate MSE
mean(model_summ$residuals^2)
```

ğ›ƒ is the "Estimated x" above, which x=-0.28 means that it has slightly negative correlations between x and y.

### 2d. (15 points) Show the residual plot and the normal plot. Make your comments.

Hint: You need to know the purposes of these two plots and judge whether the plots support the assumptions that

#### Residual plot

```{r}
res <- resid(lm.fit)
#produce residual vs. fitted plot
plot(fitted(lm.fit), res)

#add a horizontal line at 0 
abline(0,0)
```

Comments: Consist unstable variance

#### Normal plot

```{r}
# Load package, MASS
# library(MASS)
qqnorm(y)
qqline(y)
```

Comments: æœ‰å•é¡Œ (åé›¢å¸¸æ…‹)
